\vita
\singlespace
\begin{list}
{}
{\setlength
   {\labelwidth}{1in}
    \setlength{\leftmargin}{0.8in}
    \setlength{\labelsep}{.2in}
    \setlength{\itemsep}{0.2in}
    \setlength{\rightmargin}{\leftmargin}}

\item[Name\hfill] ABM Musa

\item[Education\hfill] Ph.D., Computer Science, University of Illinois at Chicago, 2017.

B.S., Computer Science and Engineering, Bangladesh University of Engineering and Technology, 2008.

\item[Publications\hfill] 
A.B.M. Musa, James Biagioni and Jakob Eriksson, “Trading Off Accuracy, Timeliness, and Uplink Usage in Online GPS Tracking,” in IEEE Transactions on Mobile Computing (TMC), vol. 15, no. 8, pp. 2124--2136, Aug. 1 2016.

James Biagioni, A.B.M. Musa, and Jakob Eriksson, “Thrifty Tracking: Online GPS Tracking with Low Data Uplink Usage”, In Proceedings of the 21st ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems (SIGSPATIAL’13). ACM, New York, NY, USA, 496--499.

A.B.M. Musa and Jakob Eriksson. “Tracking unmodified smartphones using Wi-Fi monitors”, In Proceedings of the 10th ACM Conference on Embedded Network Sensor Systems (SenSys ’12). ACM, New York, NY, USA, 281--294.

A.B.M. Musa, Jakob Eriksson, “Demo: WiFlow: Real-time Travel Time Estimation using Wi-Fi Monitors”, In Proceedings of the 9th ACM Conference on Embedded Networked Sensor Systems (SenSys ’11). ACM, New York, NY, USA, 429--430.

A.B.M. Musa, Jakob Eriksson, “On-Demand, Deploy-Anywhere Wi-Fi Diagnostics”, Demo In Proceedings of the sixteenth annual international conference on Mobile computing and networking (MobiCom ’10), ACM, New York, NY, USA.

\item[Patents\hfill]
Theodoros Salonidis, A.B.M. Musa, Seraphin B. Calo, Murtaza Jafar, Executing Data Stream Processing Applications in Dynamic Network Environments, International Business Machines Corporation, US20160156514 (2016).

Lenin Ravindranath, Victor Bahl, A.B.M. Musa, and David Chu, Application-centric Socialization, Microsoft Corporation, US20140280443 (2014).


\item[Awards\hfill]
Third place in UIC research forum competition among Engineering and Physical Science (2011)

Dean’s List for excellent academic performance in BUET (2004--2007)

University Merit Scholarship at BUET (2003)


\item[Service\hfill] 

Reviewer for IEEE Transactions on Intelligent Transportation Systems (2016--2017) 

Reviewer for International Journal for Geographical Information Science (2017) 

Treasurer at UIC Computer Science Graduate Student Association (2012--2013)

\end{list}

%% \begin{center}
%%  \Large{Tim Merrifield}
%%  \end{center}.
%%  \section*{Education}
%%  Bachelor of Science in Computer Science - Ohio University, Athens Ohio (2004))

%% \section*{Research Experience}
%% \begin{itemize}
%% \item \textbf{BITS Networking Lab, UIC}: Research Assistant ( May 2009 - Present)
%% \end{itemize}

%% \section*{Professional Experience}
%% \begin{itemize}
%% \item \textbf{Argonne National Laboratory, Decision and Information Sciences Division}: Software Engineer (January 2010 - Present )
%% \item \textbf{ShopLocal LLC}: Software Engineer (March 2005 - December 2009 )
%% \end{itemize}




%% \renewcommand{\baselinestretch}{1.0}
%% \linespread{1.0}
%% \noindent \begin{tabular}{@{} l l}

%%  \textbf{Education}  & Ph.D., Computer Science, University of Illinois at Chicago, 2017. \\
%%      & B.S., Computer Science, Bangladesh University of Eng. and Tech., 2008. \\
%%      & \\
%%  \Large{Dissertation}    & ``Title of Dissertation" \\
%%     & \parbox{5.0in}{Short description/summary of research and estimation techniques. This can be several lines long because of the paragraph box.}\\
%%     & \\
%%  \Large{Research}    & \textbf{Department, University} \\
%%      & Postdoctoral Research Associate \\
%%      & Project: Title of Research \\
%%      & \\
%%   \Large{Teaching}   & \textbf{Department, University} \\
%%      & Instructor, Fundamentals of the Global Economy, 2016 \\
%%      & \\
%%      &\textbf{Department, University} \\
%%      & Job Title, Course Name, 2014-2015 \\
%%      & Job Title, Course Name, 2012-2014 \\
%%      & \\
%%      & \textbf{Department, University} \\
%%      & Job Title, Course Name, 2013 \\
%%      & Job Title, Course Name, 2013 \\
%%      & \\
%%  \Large{Awards and }    & \textbf{Graduate Student Teacher of the Year, Department} \\
%%   \Large{Fellowships}   & Course Name, 2014-2015 \\
%%      & \\
%%      & \textbf{Fulbright Scholarship} \\
%%      & City, Country, 2006-2009 \\
%%      & \\
%%   \Large{Languages}   & English (native), German (advanced) \\
%% \Large{and Skills}    & Stata, \LaTeX, Eviews, Mathematica  \\
%% \end{tabular}





%% %\begin{table}
%% \begin{tabularx}
%% %\centering
%% \begin{tabular}{\linewidth}{l X}

%% \textbf{Name} & ABM Musa \\

%% \textbf{Education}  &  PhD, Computer Science, University of Illinois at Chicago, 2017  \\
%% ``" & BS, Computer Science, Bangladesh University of Eng. and Tech., 2008  \\

%% \textbf{Publications} & A.B.M. Musa, James Biagioni and Jakob Eriksson, “Trading Off Accuracy, Timeliness, and Uplink Usage in Online GPS Tracking,” in IEEE Transactions on Mobile Computing, vol. 15, no. 8, pp. 2124-2136, Aug. 1 2016.

%% \end{tabularx}
%% %\end{tabular}
%% \label{tab:vita}
%% \end{table}
